### 2020-04-21 Thesis-Chapter2-Background.tex
Work on EA types

% There are several types of approaches:
% TODO: after defense, create table of these and reference it in \prop lists below. This is better than sorting by
% historical origin.
% - Allow strong encryption (anyone with the users' private keys can see it)
% - Disallow encryption (anyone can see it)
% - Make encryption sufficiently weak, e.g. limit key length (anyone with enough CPU can see it)
% - Require use of backdoored algorithms, security via obscurity (anyone with the secret knowledge can see it)
% - Allow any encryption, just be able to provide keys (anyone with the extra keys can see it)
%   - Store extra in gov't DBs, in corporate DBs, in third-party DBs, on blockchain, in secure HW on device
%   - Split the key and store it multiple places
% - Use some alternative path
%   - Coerced passwords, finding unencrypted copies, seizing devices while unlocked, lawful hacking

There are several technical approaches to \ac{EA}. This section breaks down these approaches according to those
originating from \ac{the-cw1}, \ac{the-cw2}, and those that side-step the issue by using non-technical means to acquire
plaintext.

\subsection{Historical Approaches}

Historical approaches and proposals out of \ac{the-cw1} that saw various amounts of support.

\newcommand{\propsstart}[0]{\begin{itemize}}
% \newcommand{\prop}[2]{\item \textbf{#1} \cite{#2}} % Proposal name, citation
\newcommand{\prop}[3]{ % Name, citation, description
    \item \textbf{#1} \cite{#2} \nopagebreak

    \vspace{0.5\baselineskip} \parbox{\linewidth}{#3} \vspace{0.5\baselineskip}
}
\newcommand{\propsend}{\end{itemize}}

\propsstart
    \prop{Clipper chip/third-party key escrow}{press_1993}{}
% toasted by \cite{blaze_protocol_1994}
    \prop{Oblivious key escrow}{goos_oblivious_1996}{}
    \prop{Partial key escrow}{denning_taxonomy_1996}{}
\propsend

\subsection{Modern Proposals}

Recent proposals out of \ac{the-cw2} that have various levels of support.

\propsstart
    \prop{CLEAR}{ozzie_2018}{}
    \prop{Device escrow with HW}{savage_lawful_2018}{}
    \prop{Computational, blockchain approaches}{phan_key_2017}{}
\propsend

@@

\propsstart
    \prop{\Ac{lawful-hacking}}{nguyen_lawful_2017}{}
% see also \cite{soesanto_2018} \cite{kerr_encryption_2017}
    \prop{Forced password disclosure}{kerr_encryption_2017}{}
% see also \cite{bittenbender_2019}
    \prop{Alternative paths to plaintext}{kerr_encryption_2017}{}
% access device while unlocked; find copies elsewhere
\propsend

>>>>

% There are several types of approaches:
% TODO: my selections here are also rather sparse. Create another appendix? (I love work). Possibly create table of
% properties below, similar to denning_taxonomy_1996
% - Allow strong encryption (anyone with the users' private keys can see it)
% - Disallow encryption (anyone can see it)
% - Make encryption sufficiently weak, e.g. limit key length (anyone with enough CPU can see it)
% - Require use of backdoored algorithms, security via obscurity (anyone with the secret knowledge can see it)
% - Allow any encryption, just be able to provide keys (anyone with the extra keys can see it)
%   - Store extra in gov't DBs, in corporate DBs, in third-party DBs, on blockchain, in secure HW on device
%   - Split the key and store it multiple places
%   - See denning_taxonomy_1996
% - Use some alternative path
%   - Coerced passwords, finding unencrypted copies, seizing devices while unlocked, lawful hacking

% Lesson: the problem is _not_ cryptographically storing and splitting key recovery information. It's keeping those keys
%   safe! If you can sit on recorded data and wait for the keys to get leaked, which they will...

% Moving forward, what are the elements that are needed for a feasible EA system? (1) White-box-secure ways of producing
% key recovery information. Do the protocols exist? EES failed. Needs to be rock solid. (2) Dispersed key recovery
% information. (3) A robust, antifragile, inherently secure means of protecting those keys, and perhaps decaying them over
% time (https://en.wikipedia.org/wiki/Data_degradation).

There are several technical approaches to \ac{EA}. This section breaks down these approaches according to their basic
approach to \ac{key-escrow}, to cryptographic recovery without a key, or to side-stepping the issue by using
non-technical means to acquire plaintext.

\newcommand{\propsstart}[0]{\begin{itemize}}
\newcommand{\prop}[2]{ % Name, description
    \item \textbf{#1} \nopagebreak

    \vspace{0.5\baselineskip} \parbox{\linewidth}{#2} \vspace{0.5\baselineskip}
}
\newcommand{\propsend}{\end{itemize}}

\subsection{Types of Key Escrow}

The most obvious approach to \ac{EA} is to store additional copies of the encrypting keys, or information that can be
used to derive additional copies. This approach is called \ac{key-escrow}. There are several classes of key escrow.

\propsstart
    \prop{Trusted-party key escrow}{

\cite{denning_taxonomy_1996}
\ac{clipperchip} \cite{blaze_protocol_1994}
% The technical approach used by the \ac{clipperchip} secret protocol hardware enabled split-key government escrow.

    \prop{Distributed key escrow}{

\cite{goos_oblivious_1996}
\cite{phan_key_2017}

    \prop{Device key escrow}{

\cite{savage_lawful_2018}
\cite{ozzie_2018}

}
\propsend

\subsection{Non-Escrow Cryptographic Recovery}

Though key recovery is the most discussed \ac{EA} approach, alternative technical means have been proposed.

\propsstart
    \prop{Translucent Cryptography}{

\cite{bellare_translucent_1996}

}
\propsend

@@

\propsstart
    \prop{\Ac{lawful-hacking}}{

\cite{nguyen_lawful_2017}
\cite{soesanto_2018}
\cite{kerr_encryption_2017}

    \prop{Forced password disclosure}{

\cite{bittenbender_2019}
\cite{kerr_encryption_2017}

    \prop{Alternative paths to plaintext}{

% access device while unlocked; find copies elsewhere
\cite{kerr_encryption_2017}

}
\propsend

### 2020-04-21 Thesis-Glossary.tex
Work on international regs
Work on EA types

\newterm{snowden}{Snowden}{
    Edward Snowden was an CIA contractor who leaked large volumes of data on NSA programs such as PRISM that performed
    mass collection of internet communications for surveillance
}
% End terms

>>>>

\newterm{snowden}{Snowden}{
    Edward Snowden was an CIA contractor who leaked large volumes of data on NSA programs such as PRISM that performed
    mass collection of internet communications for surveillance
}

\newterm{lawful-hacking}{lawful hacking}{
    An approach to digital evidence and intelligence gathering that involves deliberate computer and network
    manipulation which is ordinarily illegal but has been cleared for law enforcement and intelligence purposes
}

\newterm{key-escrow}{key escrow}{
    An approach to \ac{EA} that relies on storing additional copies of the encryption key or storing information that
    can be used to derive additional additional copies
}
% End terms
